---
output: rmarkdown::github_document
---

# docparser

Tools to Upload/Parse Documents to 'docparser' and Retrieve Extracted Results

## Description

The 'docparser' (<https://docparser.com>) service enables users to visually define extraction regions for documents then use a 'REST' 'API' endpoint (<https://dev.docparser.com/>) to upload documents and retrieve parsed results. Tools are provided to query available parsers, upload documents and retrieved parsed results.

## What's Inside The Tin

The following functions are implemented:

- `dp_parsers`:	Retrieve avilable parsers
- `dp_parse_doc`:	Parse a document with a predefined parser
- `dp_ping`:	"Ping" the docparser API
- `dp_results`:	Retrieve results from parsed documents

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/docparser")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(docparser)

# current verison
packageVersion("docparser")

```

```{r}
dp_parsers()
```

```{r}
str(
  dp_results("484c4292ab3b324b7f2b60f3f2d3149f", "jcpfgqiexwky")
)
```